outline!

### 2016-05-18 paper.tex
paper: update
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

As we have seen, Ceph provides a rich storage API and places few restrictions
on the structure of applications. So how should we go about implementing CORFU
on Ceph? Our strategy is straightforward: first we will define the entire
design space, and we will then winnow down this space using a set of targeted
benchmarks. The design space can be divided into three challenges:
selecting a strategy for log entry addressing, choosing a native I/O interface
for storing log entry content, and implementing efficient metadata management.

@@

\paragraph*{Baseline Entry Storage Performance}
We begin the process of exploring the design space by exploiting the fact that
metadata management is a complexity and performance overhead that a full
implementation must incur beyond the costs of storing log entry data.
Therefore we first explore the design space by restricting the
space to log entry addressing and log entry storage.  These two dimensions are
represented by the first two columns of Table~\ref{tab:pd-map} which describes
the entire design space. In the I/O column \emph{KV} corresponds to the
key-value interface, and the bytestream interface is represented by \emph{AP}
for an append strategy, and \emph{EX} for a strategy that writes to an
explicit bytestream offset (both described shortly).

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{.47\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{experiments/librados-sweep/jewel_ssd.png}
      \caption{1hr,1k,wr}
      \label{fig:vanilla_wr_jewel}
  \end{subfigure}\quad
  \begin{subfigure}[b]{.47\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/output.read.60min.1k.png}
      \caption{1hr,1k,rd}
      \label{fig:vanilla_rd_jewel}
  \end{subfigure}
  \caption{Ceph and OSD... gotta cram more stuff in here...}
\end{figure}

\begin{table}
\begin{tabular}{ | l | l | l | l | l |}
\hline
Map & I/O & Entry Size & Addressing & Metadata \\ \hline
\multirow{3}{*}{1:1} & KV  & Flex     & Ceph      & KV/BS \\ \cline{2-5}
                     & AP  & Flex     & Ceph/VFS  & KV/BS \\ \hline
\multirow{4}{*}{N:1} & KV  & Flex     & \multicolumn{2}{|c|}{KV/BS} \\ \cline{2-5}
                     & EX  & Fixed    & VFS       & KV/BS \\ \cline{2-5}
                     & AP  & Flex     & KV/BS     & KV/BS \\
\hline
\end{tabular}
\caption{The high-level design space of mapping CORFU log entry storage onto
the RADOS object storage system.}
\label{tab:pd-map}
\end{table}

@@

Adds in indexing and that sort of overheads.

>>>>

As we have seen, Ceph provides a rich storage API and places few restrictions
on the structure of applications. So how should we go about implementing CORFU
on Ceph? Our strategy is straightforward: first we will define the entire
design space, and then winnow down this space using a set of targeted
benchmarks. The design space can be divided into three challenges:
selecting a strategy for log entry addressing, choosing a native I/O interface
for storing log entry content, and implementing efficient metadata management.

@@

\paragraph*{Baseline Entry Storage Performance}
We begin the process of exploring the design space by exploiting the fact that
metadata management is a complexity and performance overhead that a full
implementation must incur beyond the costs of storing log entry data.
Therefore we first explore the design space by restricting the
space to log entry addressing and log entry storage (the \emph{I/O} action
shown in Figure~\ref{fig:corfu-sm}).  These two dimensions are
represented by the first two columns of Table~\ref{tab:pd-map} which describes
the entire design space. In the I/O column \emph{KV} corresponds to the
key-value interface, and the bytestream interface is represented by \emph{AP}
for an append strategy, and \emph{EX} for a strategy that writes to an
explicit bytestream offset (both described shortly).

\begin{table}[h]
\begin{tabular}{ | l | l | l | l | l |}
\hline
Map & I/O & Entry Size & Addressing & Metadata \\ \hline
\multirow{3}{*}{1:1} & KV  & Flex     & Ceph      & KV/BS \\ \cline{2-5}
                     & AP  & Flex     & Ceph/VFS  & KV/BS \\ \hline
\multirow{4}{*}{N:1} & KV  & Flex     & \multicolumn{2}{|c|}{KV/BS} \\ \cline{2-5}
                     & EX  & Fixed    & VFS       & KV/BS \\ \cline{2-5}
                     & AP  & Flex     & KV/BS     & KV/BS \\
\hline
\end{tabular}
\caption{The high-level design space of mapping CORFU log entry storage onto
the RADOS object storage system.}
\label{tab:pd-map}
\end{table}

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{.47\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{experiments/librados-sweep/jewel_ssd.png}
      \caption{1hr,1k,wr,jewel}
      \label{fig:vanilla_wr_jewel}
  \end{subfigure}
  \begin{subfigure}[b]{.47\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/output.read.60min.1k.png}
      \caption{1hr,1k,rd,jewel}
      \label{fig:vanilla_rd_jewel}
  \end{subfigure}
  \begin{subfigure}[b]{.47\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{experiments/basic-cls-overhead/output.1024.soft.reset.png}
      \caption{1hr,1k,cls\_wr,jewel}
      \label{fig:cls_wr_jewel}
  \end{subfigure}
  \begin{subfigure}[b]{.47\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{experiments/librados-sweep/firefly_ssd.png}
      \caption{1hr,1k,wr,firefly}
      \label{fig:vanilla_wr_firefly}
  \end{subfigure}
  \caption{placeholder.}
\end{figure}

@@

The previous results show that storing log entries in the bytestream has the
potential to provide the best overall performance, but by design, those
results do not contain the real-world overheads introduced by metadata
management such as validating that requests are tagged with an up-to-date
epoch value. Having only focused on entry I/O costs, in this section we
consider the overhead of the remaining actions shown in
Figure~\ref{fig:corfu-sm}.

\begin{enumerate}
    \item {\bf Epoch guard.} Each client request must be validated against the
        current epoch. This singleton value in infrequently updated, but the
        cost of accessing the value must be incurred for every request.

    \item {\bf Per-entry metadata.} Unlike the singleton epoch value, metadata
        associated with each log position must be read, and optionally updated
        for every request. For instance the \emph{fill} operation must ensure
        that it is not applied to a log position that has already been
        written. When an operation that changes a log position is successful
        (i.e. \emph{write}, \emph{fill}, \emph{trim}) the per-entry metadata
        must also be updated to reflect the change. While the size of the
        per-entry metadata is small, it is accessed for every operation and a
        single object may manage a large number of entries.
\end{enumerate}

The design space for managing metadata can be large depending on the
application. In many cases this space is significantly reduced when the
key-value interface is used because it handles a large portion of common data
management challenges such as indexing. On the other hand, we have seen that
the bytestream can be used to achieve much higher performance when used in
lieu of the key-value database, but leaves the design space wide open.

We consider two high-level design prototypes in this paper based on both the
key-value and bytestream interfaces. The summary of performance of these
designs is shown in Figure~\ref{fig:cls_wr_jewel} where we begin by
highlighting two baseline throughputs labeled \emph{librados} and
\emph{cls\_null} that correspond to the baseline append throughput described
in the previous section, and the append throughput achieved with \emph{object
class} overhead included. We will discuss the performance of our two prototype
designs relative to the base cost of using \emph{object class} facility.

The first design is based on the key-value interface. In this design the epoch
value is stored under a fixed key, and the metadata associated with each log
entry is stored under a key derived from the log position. The expected throughput of
this design is shown in Figure~\ref{fig:cls_wr_jewel} and labeled as
\emph{cls\_full\_omap}. This result shows us that even for very small values
the cost of managing data in the key-value store introduces significant
overhead. In contrast, the unstructured bytestream interface imposes little
to no restriction on how it is used.

An obvious choice for encoding the singleton epoch value in the bytestream is
to position it at a fixed offset such as in a header. A method for indexing
entry metadata is far less obvious. Solutions span a wide design spectrum and
include approaches such as encoding a search tree into the bytestream, or
exploiting the regularity log addressing and storing a dense array that can be
efficiently indexed. While there is clearly a wide variety of approaches, we
have chosen to examine the overhead incurred by an hypothetical best-case
design in which per-entry metadata can be accessed with a single I/O. The I/O
overhead of the test includes (1) read epoch value from a fixed header
location, (2) read the per-entry metadata, and in the case of an update (3)
write the updated per-entry metadata. The expected throughput from such a
design is shown in Figure~\ref{fig:cls_wr_jewel} labeled as
\emph{cls\_full\_hdr} and performs with roughly a 6\% overhead.
